Fail Faster

### 2025-03-22 paper/paper.tex
words about why no other graph

To determine the number of random samples, we repeat the same test, but use Intel ProcessorTrace to capture processor activity.
We then count the number of invocations of \texttt{next\_int64} and average this over the number of complete generations in the trace. As expected,
the BST strategies, which achieve large speedups from \csplitmix, invoke the sampling function more: 353 times for the insertion-based strategy, and 271 for the single-pass strategy. 
STLC, which sees moderate improvements from \csplitmix, invokes \texttt{next\_int64} 211 times, and the boolean list strategy, which sees no improvement from \csplitmix, invokes it only 100 times.

>>>>

To determine the number of random samples, we repeat the same test, but use Intel ProcessorTrace \cn{} to capture a 4ms trace processor activity.
We then count the number of invocations of \texttt{next\_int64}---the actual SplitMix sampling routine---and average this over the number of complete generations in the trace. As expected,
the BST strategies, which achieve large speedups from \csplitmix, invoke the sampling function more: 353 times for the insertion-based strategy, and 271 for the single-pass strategy. 
STLC, which sees moderate improvements from \csplitmix, invokes \texttt{next\_int64} 211 times, and the boolean list strategy, which sees no improvement from \csplitmix, invokes it only 100 times\footnote{
We did not measure generator performance for \emph{un}staged generators with \csplitmix, so there is no equivalent of Figure~\ref{fig:binds} for speedup versus sampling.
}.
